E-jection fraction - Tracking how your website pumps out E-Mails

### 2016-05-13 Background/lang_aff.tex
fixing emph

\begin{itemize}
\item{\textbf{PHP}} - PHP was one of the first languages found to have this vulnerability in its implementation of the \emph{mail()} function. The early finding of this vulnerability can be attributed in part to the success and popularity of the language for creating web pages. According to w3techs \cite{W3techs}, PHP is used by 81.9\% of all the websites in existence, thereby creating the possibility of this vulnerability to be widespread.

After 13 further iterations of the language since the 4.0 release (the current version is 7.1), the \emph{mail()} function is yet to be fixed after 15 years. However, it is specified in the PHP documentation \cite{PHPDocs} that the \emph{mail()} function does not protect against this vulnerability.
A working code sample of the vulnerability, written in PHP~5.6 (latest well-supported version), is shown in  Listing~\ref{code:phpemi}.

\item{\textbf{Python}} -
A bug was filed about the vulnerability in Python's implementation of the \emph{email.header} library and its header parsing functions allowing newlines in early 2009, which was followed up with a partial patch in early 2011.

Unfortunately, the bug fix was only for the \emph{email.header} package, and thus is still prevalent in other frequently used packages such as \emph{email.parser}, where both the classic \emph{Parser()} and the newer \emph{FeedParser()} exhibit the vulnerability even in the latest versions - \emph{2.7.11} and \emph{3.5}. The bug fix was also not backported to older versions of Python. 
There is no mention of the vulnerability in the Python documentation for either library.
A working code sample of the vulnerability, written in Python 2.7.11, is shown in Listing~\ref{code:pyemi}.
\input{Background/py.tex}

>>>>

\begin{itemize}
\item{\textbf{PHP}} - PHP was one of the first languages found to have this vulnerability in its implementation of the \texttt{mail()} function. The early finding of this vulnerability can be attributed in part to the success and popularity of the language for creating web pages. According to w3techs \cite{W3techs}, PHP is used by 81.9\% of all the websites in existence, thereby creating the possibility of this vulnerability to be widespread.

After 13 further iterations of the language since the 4.0 release (the current version is 7.1), the \texttt{mail()} function is yet to be fixed after 15 years. However, it is specified in the PHP documentation \cite{PHPDocs} that the \texttt{mail()} function does not protect against this vulnerability.
A working code sample of the vulnerability, written in PHP~5.6 (latest well-supported version), is shown in  Listing~\ref{code:phpemi}.

\item{\textbf{Python}} -
A bug was filed about the vulnerability in Python's implementation of the \texttt{email.header} library and its header parsing functions allowing newlines in early 2009, which was followed up with a partial patch in early 2011.

Unfortunately, the bug fix was only for the \texttt{email.header} package, and thus is still prevalent in other frequently used packages such as \texttt{email.parser}, where both the classic \texttt{Parser()} and the newer \texttt{FeedParser()} exhibit the vulnerability even in the latest versions - \texttt{2.7.11} and \texttt{3.5}. The bug fix was also not backported to older versions of Python.
There is no mention of the vulnerability in the Python documentation for either library.
A working code sample of the vulnerability, written in Python 2.7.11, is shown in Listing~\ref{code:pyemi}.
\input{Background/py.tex}
